On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-17 main.tex
changes to is_dead code

\begin{onecolumn}
\begin{lstlisting}[
    caption=Dead State Detection Implementation,
    label=lst:dead-state-detection
]
pub struct Solver {
    // search states
    pub(super) dead_states: HashSet<Exp>,
    pub(super) explored: HashSet<Exp>,
    pub(super) uf_table: HashMap<Exp, UnionFindNode<()>>,
    // caching
    pub(super) eps_cache: LruCache<Exp, BExp>,
    pub(super) deriv_cache: LruCache<Exp, Vec<(BExp, Exp, u64)>>,
}

impl Solver {
    pub fn is_dead(&mut self, gkat: &mut Gkat, exp: &Exp) -> bool {
        let mut stack = Vec::new();
        stack.push(exp.clone());
        self.explored.clear();
        while let Some(exp) = stack.pop() {
            if self.dead_states.contains(&exp) || self.explored.contains(&exp) {
                continue;
            }
            self.explored.insert(exp.clone());
            let eps = self.epsilon(gkat, &exp);
            if eps.is_false() {
                for (_, e, _) in self.derivative(gkat, &exp) {
                    stack.push(e);
                }
            } else {
                return false;
            }
        }
        self.dead_states.extend(self.explored.iter().cloned());
        return true;
    }
}
\end{lstlisting}
\end{onecolumn}

>>>>

\begin{onecolumn}
\begin{lstlisting}[
    caption=Dead State Detection Implementation,
    label=lst:dead-state-detection
]
pub type Deriv = Vec<(BExp, Exp, u64)>;

pub struct Solver {
    // search states
    dead_states: HashSet<Exp>,
    explored: HashSet<Exp>,
    uf_table: HashMap<Exp, UnionFindNode<()>>,
    // caching
    eps_cache: LruCache<Exp, BExp>,
    deriv_cache: LruCache<Exp, Deriv>,
}

impl Solver {
    #[inline]
    pub fn known_dead(&self, exp: &Exp) -> bool {
        self.dead_states.contains(&exp)
    }

    pub fn is_dead(&mut self, gkat: &mut Gkat, exp: &Exp) -> bool {
        let mut stack = Vec::new();
        stack.push(exp.clone());
        self.explored.clear();
        while let Some(exp) = stack.pop() {
            if self.known_dead(&exp) || self.explored.contains(&exp) {
                continue;
            }
            self.explored.insert(exp.clone());
            let eps = self.epsilon(gkat, &exp);
            if eps.is_false() {
                for (b, e, _) in self.derivative(gkat, &exp) {
                    // check is not strictly needed due to eager-pruning
                    if b.is_false() {
                        continue;
                    }
                    stack.push(e);
                }
            } else {
                return false;
            }
        }
        self.dead_states.extend(self.explored.iter().cloned());
        return true;
    }
}
\end{lstlisting}
\end{onecolumn}
